If space is flat, we may choose a system of coordinates that is rectilinear and then the $g_{\mu\nu}$ are constant. The 
tensor $R_{\mu\nu\rho\sigma}$ then vanishes.

Conversely, if $R_{\mu\nu\rho\sigma}$ vanishes, one can prove that the space is flat. Let us take a vector $A_{\mu}$ 
situated at the point $x$ and shift it by parallel displacement to the point $x+dx$. Then shift it by parallel 
displacement to the point $x+dx+\delta x$. If $R_{\mu\nu\rho\sigma}$ vanishes, he result must be the same as if we had 
shifted it first from $x$ to $x+\delta x$, then to $x+\delta x+ dx$. Thus we can shift the vector to a distant point and 
the result we get is independent of the path to the distant point. Therefore, if we shift the original vector $A_{\mu}$ 
at $x$ to all points by parallel displacement, we get a vector field that satisfies $A_{\mu:\nu}=0$, or
\begin{equation}
 \label{ecuacion 12.1}
 A_{\mu,\nu} = \Gamma^{\alpha}_{\mu\nu}.
\end{equation}

Can such a vector field be the gradient of a scalar? Let us put $A_{\mu} = 
S_{\mu}$ in (\ref{ecuacion 12.1}). We get 
\begin{equation}
 \label{ecuacion 12.2}
 S_{,\mu\nu} = \Gamma^{\alpha}_{\mu\nu} S_{\alpha}
\end{equation}
By virtue of the symmetry of $\Gamma^{\alpha}_{\mu\nu}$ in the lower suffixes, we have the same value for $S_{,\mu\nu}$ 
as $S_{,\nu\mu}$ and the equations (\ref{ecuacion 12.2}) are integrable.

Let us take four independent scalars satisfying (\ref{ecuacion 12.2}) and let them to be the coordinates $x^{\alpha'}$ 
of a new system of coordinates. Then
\[
 x^{\alpha'}_{,\mu\nu} = \Gamma^{\sigma}_{\mu\nu} x^{\alpha'}_{,\sigma}.
\]

According the transformation law (\ref{ecuacion 3.7}),
\[
g_{\mu\lambda} = g_{\alpha'\beta'}x^{\alpha'}_{,\mu}x^{\beta'}_{,\lambda}.
\]
Differentiating this equation with respect to $x^{\nu}$, we get
\[
\begin{array}{rcl}
 g_{\mu\lambda,\nu} - g_{\alpha'\beta',\nu}x^{\alpha'}_{,\mu}x^{\beta'}_{,\lambda} & = & 
    g_{\alpha'\beta'}\left(x^{\alpha'}_{,\mu\nu}x^{\beta'}_{,\lambda} 
    + x^{\alpha'}_{,\mu}x^{\beta'}_{,\lambda\nu} \right) \\
    & = & g_{\alpha'\beta'}\left(
    \Gamma^{\sigma}_{\mu\nu} x^{\alpha'}_{,\sigma} x^{\beta'}_{,\lambda} 
    + x^{\alpha'}_{,\mu} \Gamma^{\sigma}_{\lambda\nu} x^{\beta'}_{,\sigma}
    \right)\\
    & = & g_{\sigma\lambda} \Gamma^{\sigma}_{\mu\nu} + g_{\mu\sigma} \Gamma^{\sigma}_{\lambda\nu}\\
    & = & \Gamma_{\lambda\mu\nu} + \Gamma_{\mu\lambda\nu} = g_{\mu\lambda,\nu}
\end{array}
\]
from (\ref{ecuacion 7.6}). Thus
\[
g_{\alpha'\beta',\nu}x^{\alpha'}_{,\mu}x^{\beta'}_{,\lambda} = 0.
\]
It follows that $g_{\alpha'\beta',\nu}=0$. Referred to the new system of coordinates, the fundamental tensor is 
constant. Thus we have flat space referred to rectilinear coordinates.
