Let us consider a static gravitational field and refer it to a static coordinate system. The $g_{\mu\nu}$ are then 
constant in time, $g_{\mu\nu,0} = 0$. Further, we must have 
\[
 g_{m0} = 0, \, \left( m=1,\cdots,3 \right) .
\]
This leads to
\[
 g^{m0} = 0, \, g^{00} = (g_{00})^{-1},
\]
and $g^{mn}$ is the reciprocal matrix to $g_{mn}$. Roman suffixes like $m$ and $n$ always take on the values 1, 2, 3. 
We find that $\Gamma_{m0n} = 0$ and hence also $\Gamma^{m}_{0n}=0$.

Let us take a particle that is moving slowly, compared with the velocity of light. Then $v^m$ is a small quantity, of 
the first order(\footnote{compared to $v^0$.}). With neglect of second order quantities,
\begin{equation}
 \label{ecuacion 16.1}
 g_{00} {v^{0}}^2 = 1.
\end{equation}
The particle will move along a geodesic. With neglect of second-order quantities, the equation (\ref{ecuacion 8.3}) 
gives
\[
\begin{array}{rcl}
 \frac{dv^m}{ds} & = & -\Gamma^m_{00}{v^0}^2 = -g^{mn} \Gamma_{n00}{v^0}^2\\
                 & = & = \frac{1}{2} g^{mn}g_{00,n} {v^0}^2. 
\end{array}
\]
Now
\[
 \frac{dv^m}{ds} = \frac{dv^m}{dx^0} \frac{dx^0}{ds} = frac{dv^m}{dx^0}v^0
\]
to the first order. Thus
\begin{equation}
 \label{ecuacion 16.2}
 \frac{dv^m}{dx^0} = \frac{1}{2} g^{mn}g_{00,n}v^0 = g^{mn}\left( {g_{00}}^{1/2} \right)_{,n}
\end{equation}
with the help of (\ref{ecuacion 16.1}). Since the $g_{\mu\nu}$ are independent of $x^0$, we may lower the suffix $m$ 
here and get
\begin{equation}
 \label{ecuacion 16.3}
 \frac{dv^m}{dx^0} = \left( {g_{00}}^{1/2} \right)_{,m} .
\end{equation}

We see that the particle moves as thought it were under the influence of a potential $\left({g_{00}}^{1/2}\right)$. We 
have not used Einstein's law to obtain this result. We now use Einstein's law to obtain a condition for the potential, 
so that it can be compared with Newton's.

Let us suppose that the gravitational field is weak, so that the curvature of space is small. Then we may choose our 
coordinate system so that the curvature of the coordinate lines (each with three $x$'s constant) is small. Under those 
conditions the $g_{\mu\nu}$ are approximately constant, and $g_{\mu\nu,\sigma}$ and all the Christoffel symbols are 
small. If we count them of the first order and neglect second-order quantities, Einstein's law (\ref{ecuacion 15.1}) 
becomes, from (\ref{ecuacion 14.4})
\[
 \Gamma^{\alpha}_{\mu\alpha,\nu} - \Gamma^{\alpha}_{\mu\nu,\alpha} = 0.
\]
We can evaluate this most conveniently by contracting (\ref{ecuacion 11.6}) with $\rho$ and $\mu$ interchanged and 
neglecting second-order terms. The result is
\begin{equation}
 \label{ecuacion 16.4}
 g^{\rho\sigma} \left( 
      g_{\rho\sigma,\mu\nu} 
    - g_{\nu\sigma,\mu\rho} 
    - g_{\mu\rho,\nu\sigma} 
    + g_{\mu\nu,\rho\sigma}  \right) = 0.
\end{equation}

Now take $\mu=\nu=0$ and use the condition that the $g_{\mu\nu}$ are independent of $x^0$. We get
\begin{equation}
 \label{ecuacion 16.5}
 g^{mn} g_{00,mn} = 0.
\end{equation}

The D'Alembert equation (10.9) becomes, in the weak field approximation,
\[
 g^{\mu\mu} V{,\mu\nu} = 0.
\]
In the static case, this reduces to Laplace's equation
\[
 g^{mn} V_{,mn} = 0.
\]

We may choose our unit of time so that $g_{00}$ is approximately unity. Then we may put
\begin{equation}
 \label{ecuacion 16.6}
 g_{00} = 1 + 2 V,
\end{equation}
with $V$ small. We get ${g_{00}}^{1/2} = 1 + V$ and V becomes the potential. It satisfies the Laplace equation so that 
it can be identified with the Newtonian potential, equal to $-m/r$ for a mass $m$ at the origin. To check the sign we 
see that (\ref{ecuacion 16.2}) leads to
\[
 \mbox{acceleration} = - \mbox{ grad } V,
\]
since $g^{mn}$ has the diagonal elements approximately $-1$.

We see that Einstein's law of gravitation goes over to Newton's when the field is weak and when it is 
static.(\footnote{This is not exactly a proof. From the requirement of covariance and the realization that Einstein's 
equation are a quasilinear system of second order partial equations, considering that Laplace's operator is the only 
differential linear operator of the second-degree that satisfies the requirements of homogeneity and isotropy of 
space, this result is a formal property of the theory. A proof that Einstein's theory reduces to Newton's theory will 
require to prove that it leads to Poison's equation.}) The successes of the Newtonian theory in explaining the motions 
of the planets can this be preserved. The static approximation is a good one because the velocities of the planets are 
all small compared to the with the velocity of light (\footnote{In the local system of reference.}). The weak field 
approximation is a good one because the space is very nearly flat. Let us consider some orders of magnitude.

The value of $V$ on the surface of earth turns out to be of the order of $10^{-9}$, thus $g_{00}$ given by 
(\ref{ecuacion 16.6}) is very close to one. Even so, its difference from one is big enough to produce the important 
gravitational effects that we see on earth. Taking the radius of earth to be of the order of $10^9$ centimeters, we 
find that $g_{00,m}$ is of the order of $10^{-18}\mbox{cm}^{-1}$. The departure from flatness is thus extremely small. 
However, this has to be multiplied by the square of the speed of light, namely $9\times 10^{10} \mbox{cm/sec}^2$, to 
give the acceleration of gravity at earth's surface. Thus, this acceleration, about $10^3 \mbox{cm}/\mbox{sec}^2$, is 
quite appreciable, even thought the department of flatness is far too small to be observed directly.




