The Einstein equations for empty space are nonlinear and are therefore very complicated, and it is difficult to get 
accurate solutions of them. There is, however, a special case which can be solved without too much trouble; namely the 
static spherically symmetric field produced by a spherically symmetric body at rest.

The static condition means that, with a static coordinate system, the $g_{\mu\nu}$ are independent of the time $x^0$ or 
$t$ and also $g_{0m}$(\footnote{Making the assumption that all intervals of the form $(\delta x^0,0,0,0)$ are temporal 
and all interval of the form $(0,\delta x^1, \delta x^2, \delta x^3)$ are spatial.}). The spatial coordinates may be 
taken to be spherical polar coordinates $x^1 = r,\,x^2=\theta,\,x^3=\phi$. The most general form of $ds^2$ compatible 
with spherical symmetry is
\[
 ds^2 = U dt^2 - V dr^2 -W r^2(d\theta^2 + \sin^2\theta d\phi^2),
\]
where $U$, $V$, and $W$ are functions of $r$ only. We may replace $r$ by any function of $r$ without disturbing the 
spherical symmetry. We use this freedom to simplify things as much as possible, and the most convenient arrangement is 
to have $W=1$. The expression for $ds^2$ may then be written as 
\begin{equation}
 \label{ecuacion 18.1}
 ds^2 = e^{2\nu} dt^2 - e^{2\lambda} dr^2 - r^2 d\theta^2 - r^2 \sin^2 \theta d\phi^2,
\end{equation}
with $\nu$ and $\lambda$ functions of $r$ only. They must be chosen to satisfy the Einstein equations. We can read off 
the values of the $g_{\mu\nu}$ from (\ref{ecuacion 18.1}), namely,
\[
\begin{array}{cccc}
 g_00 = e^{2\nu}, & g_{11} = e^{-2\lambda}, & g_{22} = -r^2, & g_{33} = - r^2 \sin^2\theta,
\end{array}
\]
and 
\[
g_{\mu\nu} = 0 \mbox{ for } \mu \ne \nu .
\]
We find
\[
   \begin{array}{cccc}
   g^{00} = e^{-2\nu}, & g_{11} = e^{-2\lambda}, & g^{22} = -r^2, &  g^{33} = -r^{-2} \sin^{-2} 
\theta,
   \end{array}
\]
and
\[
 g^{\mu\nu} = 0 \mbox{ for } \mu \ne \nu .
\]

It is now necessary to calculate all the Christoffel symbols $\Gamma^\sigma_{\mu\nu}$. Many of them vanish. The ones 
that do not are(\footnote{With primes denoting differentiation with respect to $r$.}):
\[
 \begin{array}{ll}
   \Gamma^1_{00} = \nu' e^{2\nu - 2 \lambda}       & \Gamma^0_{10} =  \nu' \\
   \Gamma^1_{11} = \lambda'                        & \Gamma^2_{12} = \Gamma^3_{13} = r^{-1}\\
   \Gamma^1_{22} = - r e^{-2\lambda}               & \Gamma^2_{23} = \cot \theta \\
   \Gamma^1_{33} = - r \sin^2 \theta e^{-2\lambda} & \Gamma^2_{33} = - \sin \theta \cos \theta
 \end{array}
\]
These expressions are to be substituted in (\ref{ecuacion 14.4}). The results are
\begin{equation}
 \label{ecuacion 18.2}
 R_{00} = \left( - \nu'' + \lambda' \nu' - {\nu'}^2 - \frac{2 \nu'}{r} \right) e^{2 \nu - 2 \lambda},
\end{equation}
\begin{equation}
 \label{ecuacion 18.3}
 R_{11} = \nu'' - \lambda' \nu' + {\nu'}^2 - \frac{2 \lambda'}{r},
\end{equation}
\begin{equation}
 \label{ecuacion 18.4}
 R_{22} = (1 + r \nu' - r \lambda' ) e^{-2\lambda} -1,
\end{equation}
\[
 R_{33} = R_{22} \sin^2 \theta,
\]
with the other components of $R_{\mu\nu}$ vanishing.

Einstein's law of gravitation requires these expressions to vanish. The vanishing of (\ref{ecuacion 18.2}) and 
(\ref{ecuacion 18.3}) leads to
\[
 \lambda' + \nu' = 0. 
\]
For large values of $r$ the space must approximate to being flat, so that $\lambda$ and $\nu$ both tend to zero as 
$r\rightarrow \infty$. It follows that
\[
 \lambda + \nu = 0.
\]
The vanishing of (\ref{ecuacion 18.4}) now gives
\[
 (1 + 2 r \nu') e^{2\nu} = 1
\]
or
\[
 \left( r e^{2\nu}\right)' = 1.
\]
Thus 
\[
 r e^{2\nu} = r - 2m,
\]
where $m$ is a constant of integration. This also makes (\ref{ecuacion 18.2}) and (\ref{ecuacion 18.3}) vanish. We now 
get
\begin{equation}
 \label{ecuacion 18.5}
 g_{00} = 1 - \frac{2 m}{r}
\end{equation}




