The vector $A^\mu$ has the covariant divergence $A^\mu_{;\mu}$, which is a scalar. We have
\[
    {A^\mu}_{;\mu} = A^\mu_{,\mu} + \Gamma^\mu_{\nu\mu} A^\nu = A^\mu_{,\mu}+\sqrt{}^{-1}\sqrt{}_{,\nu}A^\nu.
\]
Thus
\begin{equation}
 \label{ecuacion 21.1}
 A^\mu_{;\mu} \sqrt{} = \left( A^\mu \sqrt{} \right)_{,\mu}.
\end{equation}

We can put $A^\mu_{;\mu}\sqrt{}$ for $S$ in (\ref{ecuacion 20.4}), and we get the invariant
\[
 \int {A^\mu_{;\mu}\sqrt{} d^4 x}
  = \int { \left(A^\mu \sqrt{}\right)_{,\mu} d^4 x}.
\]
If the integral is taken over a finite (four-dimensional) volume, the right hand side can be converted by Gauss's 
theorem to an integral over the boundary surface (three-dimensional) of that volume.

If $A^\mu_{;\mu}=0$, we have 
\begin{equation}
 \label{ecuacion 21.2}
 \left( A^\mu \sqrt{}\right)_{,\mu} = 0
\end{equation}
and this gives us a conservation law; namely, the conservation of a fluid whose density is $A^0\sqrt{}$ and whose flow 
is given by the three-dimensional vector $A^m\sqrt{}(m=1,2,3)$. We may integrate (\ref{ecuacion 21.2}) over a 
three-dimensional volume $V$ lying at a fixed time $x^0$(\footnote{I sense here an error of method because Dirac makes 
the assumption that $x^0$ is strictly temporal.}). The result is
\[
\begin{array}{rcl}
    \left(\int{A^0\sqrt{}d^3x}\right)_{,0} & = & - \int{\left(A^m\right)_{,m}d^3 x} \\
                               & = & \mbox{ surface integral over boundary of } V
\end{array} 
\]
If there is no current in the boundary of $V$, $\int{A^0\sqrt{}d^3x}$ is constant. 

Those results for a vector $A^\mu$ cannot be taken over to a a tensor with more than on suffix, in general. Take a two 
suffix tensor $Y^{\mu\nu}$. In flat space we can use Gauss's theorem to express $\int{{Y^{\mu\nu}}_{,\nu}dx^4}$ as a 
surface integral, but in curved space we cannot in general express $\int{{Y^{\mu\nu}}_{;\nu}\sqrt{}dx^4}$ as a surface 
integral. An exception occurs for an antisymmetrical tensor $F^{\mu\nu} = -F^{\nu\mu}$.

In this case we have
\[
 {F^{\mu\nu}}_{;\sigma} = {F^{\mu\nu}}_{,\sigma} +
 \Gamma^{\mu}_{\sigma\rho} F^{\rho\nu} +
 \Gamma^{\nu}_{\sigma\rho} F^{\mu\rho}
\]
so
\[
 \begin{array}{rcl}
  {F^{\mu\nu}}_{;\nu} & = & {F^{\mu\nu}}_{,\nu} +
 \Gamma^{\mu}_{\nu\rho} F^{\rho\nu} +
 \Gamma^{\nu}_{\nu\rho} F^{\mu\rho} \\
 & = & {F^{\mu\nu}}_{,\nu} + \sqrt{}^{-1} \sqrt{}_{,\rho} F^{\mu\rho}
 \end{array}
\]
from (\ref{ecuacion 20.6}) (\footnote{And the fact that $\Gamma^{\mu}_{\nu\rho} F^{\rho\nu} \equiv 0$ because 
$\Gamma^{\mu}_{\nu\rho} = \Gamma^{\mu}_{\rho\nu}$.}). Thus 
\begin{equation}
 \label{ecuacion 21.3}
 {F^{\mu\nu}}_{;\nu} \sqrt{} = \left( {F^{\mu\nu} \sqrt{}} \right)_{,\nu} 
\end{equation}
Hence $\int{{F^{\mu\nu}}_{;\nu} \sqrt{}d^4x} = \mbox{ a surface integral}$, and if ${F^{\mu\nu}}_{;\nu} = 0$ we have a 
conservation law.

In the symmetrical case $Y^{\mu\nu} = Y^{\nu\mu}$ we can get a corresponding equation with an extra term, provided we 
put one of the suffixes downstairs and deal with ${{Y_\mu}^\nu}_{;\nu}$. We have
\[
 {{Y_\mu}^\nu}_{;\sigma} = {{Y_\mu}^\nu}_{,\sigma} - \Gamma^\alpha_{\mu\sigma} {{Y_\alpha}^\nu} 
 + \Gamma^\nu_{\sigma\alpha} {{Y_\mu}^\alpha}.
\]
Putting $\sigma=\nu$ and using (\ref{ecuacion 20.6}), we get
\[
  {{Y_\mu}^\nu}_{;\nu} = {{Y_\mu}^\nu}_{,\nu} 
 + \sqrt{}^{(-1)}\sqrt{}_{\alpha} {{Y_\mu}^\alpha}
 - \Gamma_{\alpha\mu\nu} {Y^{\alpha\nu}}.
\]
Since $Y^{\mu\nu}$ is symmetrical, we can replace the $\Gamma_{\alpha\mu\nu}$ in the last term by
\[
\frac{1}{2}\left( \Gamma_{\alpha\nu\mu} + \Gamma_{\nu\alpha\mu} \right) = \frac{1}{2} g_{\alpha\nu,\mu}
\]
from (7.6). Thus we get
\begin{equation}
 \label{ecuacion 21.4}
 {{Y_\mu}^\nu}_{;\nu} = {{Y_\mu}^\nu}_{,\nu} 
 +  \left( {{Y_\mu}^\nu} \sqrt{} \right)_{,\nu}
 - \frac{1}{2} g_{\alpha\beta,\mu} Y^{\alpha\beta}.
\end{equation}
For a covariant vector $A_\mu$, we have
\begin{equation}
 \label{ecuacion 21.5}
 \begin{array}{rcl}
 A_{\mu;\nu} - A_{\nu;\mu} & = & A_{\mu,\nu} - \Gamma^\rho_{\mu\nu} A_{\rho} - 
 \left( A_{\nu,\mu} - \Gamma^\rho_{\nu\mu} A_{\rho} \right)\\
 & = & A_{\mu,\nu} - A_{\nu,\mu}.
 \end{array}
\end{equation}

Let us integrate this equation over an area of the surface $x^0 = \mbox{ constant}$, $x^3 = \mbox{ constant}$. From 
Stokes theorem we get 
\begin{equation}
 \label{ecuacion 21.6}
 \begin{array}{rcl}
  \iint{\left( A_{1;2} - A_{2;1}\right)dx^1 dx^2} & = & \iint{\left( A_{1,2} - A_{2,1}\right)dx^1 dx^2}\\
  & = & \oint{ \left( A_1 dx^1 + A_2 dx^2 \right)}
 \end{array}
\end{equation}
integrated around the perimeter of the area. Thus we get an integral round a perimeter equated to a flux crossing the 
surface bounded by the perimeter.

The result must hold in all coordinate systems,not merely those for which the equations of the surface are  $x^0 = 
\mbox{ constant}$, $x^3 = \mbox{ constant}$.

To get an invariant way of writing the result, we introduce a general formula for an element of two-dimensional 
surface. If we take two small contravariant vectors $\xi^\mu$ and $\zeta^\nu$, the element of surface area that they 
subtend is determined by the antisymmetric two-index tensor
\[
 d S^{\mu\nu} = \xi^\mu \zeta^\nu - \xi^\nu \zeta^\mu,
\]
Thus, if $\xi^\mu$ has the components $0,dx^1,0,0$ and $\zeta^\nu$ has the components $0,0,dx^2,0$, then $dS^{\mu\nu}$ 
has the components
\[
 dS^{12} = dx^1 dx^2, \, dS^{21} = - dx^1 dx^2,
\]
with the other components vanishing. The left-hand side of (\ref{ecuacion 21.6}) becomes
\[
 \iint{A_{\mu;\nu}dS^{\mu;\nu}}.
\]
The right hand side is evidently $\oint{A_\mu dx^\mu}$, so the formula becomes (\footnote{The first integral on the 
surface and the second on the perimeter.})
\begin{equation}
 \label{ecuacion 21.7}
 \frac{1}{2} \iint{\left(A_{\mu;\nu} - A_{\nu;\mu}\right)dS^{\mu\nu}} = \oint A_\mu dx^\mu.
\end{equation}
