
We can have a quantity $N^{\mu}_{\nu\rho\cdots}$ with various up and down 
suffixes, which is not a tensor. If it is a tensor, it must transform under a 
change of coordinate system according to the law exemplified by (\ref{ecuacion 
3.6}). With any other law it is a nontensor. A tensor has the property that if 
all the components vanish in a system of coordinates, they vanish in every 
system of coordinates. This may not hold for a nontensor.

For a nontensor we can raise and lower suffixes by the same rules as for a 
tensor. Thus, for example,
\[
    g^{\alpha\nu} {N^{\mu}}_{\nu\rho} = {N^{\mu\alpha}}_{\rho}.
\]
The consistency of these rules is quite independent of the transformation laws 
to a different system of coordinates. Similarly, we can contract a nontensor by 
putting an upper and lower suffix equal.

We may have tensors and nontensors apparing together in the same equation. The 
rules for balancing suffixes apply  equally to tensors and nontensors.

\subsection{The Quotient Theorem}
Suppose that $P_{\lambda\mu\nu}$ is such that $A^\lambda P_{\lambda\mu\nu}$ is 
a tensor \emph{for any vector} $A^\lambda$. Then $P_{\lambda\mu\nu}$ is a 
tensor.

To prove it, write $A^\lambda P_{\lambda\mu\nu} = Q_{\mu\nu}$. We are given 
that this is a tensor; therefore
\[
 Q_{\beta\gamma} = Q_{\mu'\nu'} x^{\mu'}_{,\beta} x^{\nu'}_{,\gamma}.
\]

Thus 
\[
A^\alpha P_{\alpha\beta\gamma} = A^{\lambda'}P_{\lambda'\mu'\nu'}
        x^{\mu'}_{,\beta}x^{\nu'}_{,\gamma}.
\]
Since $A^\lambda$ is a vector, we have from (\ref{ecuacion 3.2}),
\[
 A^{\lambda'} = A^\alpha x^{\lambda'}_{,\alpha'}.
\]
So
\[
A^\alpha P_{\alpha\beta\gamma} = 
A^\alpha 
x^{\lambda'}_{,\alpha}P_{\lambda'\mu'\nu'} x^{\mu'}_{,\beta}x^{\nu'}_{,\gamma}.
\]
This equation must hold for all values of $A^\alpha$, so
\[
P_{\alpha\beta\gamma} = 
P_{\lambda'\mu'\nu'} x^{\lambda'}_{,\alpha} x^{\mu'}_{,\beta}x^{\nu'}_{,\gamma}.
\]
showing that $P_{\alpha\beta\gamma}$ is a tensor.

The theorem also holds is $P_{\alpha\beta\gamma}$ is replaced by a quantity 
with any number of suffixes, and if some of the suffixes are upstairs.

